Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
add some reference and change the content in result part in the paper

#loading packages
#install.packages("opendatatoronto")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("here")
#install.packages("kableExtra")
library(opendatatoronto)
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)
```

@@

```
After loading the dataset using the R programming language [@citeR] and the `opendatatoronto` package [@citeopendatatoronto], the `tidyverse` [@citetidyverse] package was used to generate graphs.

>>>>

#loading packages
#install.packages("opendatatoronto")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("here")
library(opendatatoronto)
library(tidyverse)
library(here)
library(knitr)
```

@@

```
After loading the dataset using the R programming language [@citeR] to do data analyse with the following package:  `opendatatoronto` [@citeopendatatoronto],  `tidyverse` [@citetidyverse],  `here` [@citehere], `knitr` [@citeknitr].
